Multi-Robot Probabilistic Mapping and Exploration

### 2018-07-05 Dissertation/Thesis/tex/results.tex
tylee edit

\section{Pioneer Ground Vehicle Tests}
\label{sec:PioneerNRL}

@@

\subsection{Hardware Configuration}
The Pioneer 3 ground robot is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provide the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

@@

The software structure is similar to ROS nodes Section \ref{sec:Ae2DNumExamples}, which simply involves a mapping node, an exploration node, and a visualization node using ``OpenGL'' libraries. The only differences are eliminating the simulator (Stage) and adding synchronization among the sensors, which is of high importance to the proposed occupancy grid mapping approach. Any time delay between the robot pose estimation and the sensor depth readings can cause conflicting information, which may be harmful to the probabilistic map. Thus, ROS approximate message filters are applied such that the pose from Vicon Tracker ($100$Hz) and the Microsoft Kinect ($30$Hz) are nearly synchronized, which provides validity of the assumption that the measurement ray positions and directions are known deterministically.

\subsection{Exploring and Mapping a 2D Environment}
The environment consists of Styrofoam walls on a flat floor. The perimeter is rectangular, with several obstacles and angled walls (see Figure \ref{fig:ExpSetupPhoto}). The robot autonomously explored the space using the complete Cartesian searching approach, and Dijkstra's algorithm provides collision-free waypoints to the optimal future poses. Based on these waypoints, a constrained least squares polynomial fitting generates a smooth trajectory to follow the waypoints with fixed velocity. Finally, a simple controller is implemented such that the Pioneer follows the trajectory by moving and orienting toward the desired robot location $1$ sec in the future.

@@

\section{Quadrotor Exploration of a Large Room}
\label{sec:QuadrotorNRL}

@@

The U.S. Naval Research Laboratory (NRL) has a large experimental space for testing known as the Laboratory for Autonomous Systems Research (LASR). Here, the experimental setup contains walls and objects to resemble a building floor plan. The perimeter walls are constructed with tan cardboard, which were suspended from $1$ m tall stanchions, and an internal wall is built with gray metal sheeting mounted to $80/20$ supports~\cite{url_8020}. Additionally, a hard flooring reflects some florescent lighting above. The objects inside the experimental environment include various trash cans, desks, and chairs in addition to a few miscellaneous objects. The map size is selected to slightly exceed the volume of the experiment such that the the x-direction (positive east) spans $0.5$ m to $10.3$ m, the y-direction (positive north) spans $-8.3$ m to $3.5$ m, and the z-direction (positive vertically up) spans $-0.15$ m to $1.5$ m. Two images of the experimental environment are displayed in Figure \ref{fig:exp3DEnvironment}.

@@

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.65\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_0min.jpg}
        		\caption{$0$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
		\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
	\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
	\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min47sec.jpg}
        		\caption{$2$ min $47$ sec (end)}
    	\end{subfigure}
	\caption{3D Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 3D occupancy grid map is overlaid with point cloud measurements. The map probabilities directly rely on the Xtion and Hokuyo measurements and the sensor stochastic properties.
	\label{fig:exp3DMap}
\end{figure}

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_0min_2D.jpg}
        		\caption{$0$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_1min_2D.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_2min_2D.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_2min47sec_2D_labeled.jpeg}
        		\caption{$2$ min $47$ sec (end)}
    	\end{subfigure}
	\caption{2D Projected Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 2D projected map is easily produced in real-time. Candidate future poses, shown by arrows, have more blue color for larger objective functions, found with expected information gains and travel distances. Collision-free waypoints (blue line) serve as input to a constrained polynomial least-squares path (light green curve) for the robot controller to follow, where the desired pose (large axes) is tracked by the onboard controller from the current robot pose (small axes).
	\label{fig:exp2DMap}
\end{figure}

>>>>

\section{2D Exploration With an Unmanned Ground Vehicle}
\label{sec:PioneerNRL}

@@

% TL: add a figure of Pioneer
\subsection{Hardware Configuration}
The Pioneer 3 ground robot is chosen for this experiment because of its reliability and simple operation. The vehicle accepts two inputs, namely linear velocity (aligned with the robot wheels) and angular velocity (about a central axis passing vertically through the robot). The robot pose is estimated via Vicon Tracker, which provides the location and attitude of a rigid body. The depth readings are obtained by a Kinect depth sensor. Since the experiment is to map and explore a 2D environment, only a single central row of the 3D Kinect depth scan provide the necessary measurements. The robot captures an experimental environment with walls constructed from Styrofoam.

@@

% add citation for OpenGL
The software structure is similar to ROS nodes Section \ref{sec:Ae2DNumExamples}, which simply involves a mapping node, an exploration node, and a visualization node using OpenGL libraries. The only differences are eliminating the simulator (Stage) and adding synchronization among the sensors, which is of high importance to the proposed occupancy grid mapping approach. Any time delay between the robot pose estimation and the sensor depth readings can cause conflicting information, which may be harmful to the probabilistic map. Thus, ROS approximate message filters are applied such that the pose from Vicon Tracker ($100$Hz) and the Microsoft Kinect ($30$Hz) are nearly synchronized, which provides validity of the assumption that the measurement ray positions and directions are known deterministically.

\subsection{Exploring and Mapping a 2D Environment}
% TL: I wish there are more photos from the experiments 
The environment consists of Styrofoam walls on a flat floor. The perimeter is rectangular, with several obstacles and angled walls (see Figure \ref{fig:ExpSetupPhoto}). The robot autonomously explored the space using the complete Cartesian searching approach, and Dijkstra's algorithm provides collision-free waypoints to the optimal future poses. Based on these waypoints, a constrained least squares polynomial fitting generates a smooth trajectory to follow the waypoints with fixed velocity. Finally, a simple controller is implemented such that the Pioneer follows the trajectory by moving and orienting toward the desired robot location $1$ sec in the future.

@@

\section{Aerial Exploration of a Large Space}
\label{sec:QuadrotorNRL}

@@

The U.S. Naval Research Laboratory (NRL) has a large experimental space for testing known as the Laboratory for Autonomous Systems Research (LASR). Here, the experimental setup contains walls and objects to resemble a building floor plan. The perimeter walls are constructed with tan cardboard, which were suspended from $1$ m tall stanchions, and an internal wall is built with gray metal sheeting mounted to $80/20$ supports~\cite{url_8020}. Additionally, a hard flooring reflects some florescent lighting above. The objects inside the experimental environment include various trash cans, desks, and chairs in addition to a few miscellaneous objects. The map size is selected to slightly exceed the volume of the experiment such that the x-direction (positive east) spans $0.5$ m to $10.3$ m, the y-direction (positive north) spans $-8.3$ m to $3.5$ m, and the z-direction (positive vertically up) spans $-0.15$ m to $1.5$ m. Two images of the experimental environment are displayed in Figure \ref{fig:exp3DEnvironment}.

@@

% TL: add figures for more time instances
\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.65\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_0min.jpg}
        		\caption{$0$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
		\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
	\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.65\columnwidth}
	\vspace*{0.01\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_ogm3D_2min47sec.jpg}
        		\caption{$2$ min $47$ sec (end)}
    	\end{subfigure}
	\caption{3D Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 3D occupancy grid map is overlaid with point cloud measurements. The map probabilities directly rely on the Xtion and Hokuyo measurements and the sensor stochastic properties.
	\label{fig:exp3DMap}
\end{figure}

% TL: add figures for more time instances
\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_0min_2D.jpg}
        		\caption{$0$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_1min_2D.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_2min_2D.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.44\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{experiment_2min47sec_2D_labeled.jpeg}
        		\caption{$2$ min $47$ sec (end)}
    	\end{subfigure}
	\caption{2D Projected Occupancy Grid Map During Level Flight Experiment}
	\medskip
	\small
	The 2D projected map is easily produced in real-time. Candidate future poses, shown by arrows, have more blue color for larger objective functions, found with expected information gains and travel distances. Collision-free waypoints (blue line) serve as input to a constrained polynomial least-squares path (light green curve) for the robot controller to follow, where the desired pose (large axes) is tracked by the onboard controller from the current robot pose (small axes).
	\label{fig:exp2DMap}
\end{figure}
